Vibration Characterisation of Strollers and\\ Cargo Bicycles for Transporting Infants\\ \vspace{2mm} \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\ \vspace{2mm} \large{Prepared for VeiligheidNL}

### 2025-01-31 main.tex
Updated the tex files to v3.

@@

% hyperref settings for better looking links
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
}

\title{
  DRAFT: v1 \\
  Vibration Characterization of Babies\\
  Transported in Strollers and Cargo Bicycles\\
  \vspace{2mm}
  \large{Prepared for VeiligheidNL}
}
\author{Gabriele Dell'Orto \and Brecht Daams \and Riender Happee \and Jason K. Moore}

@@

\section*{\centering Notice}
%
\textbf{This is a draft report. The values and results must be considered
preliminary and may change as the analysis is refined and rechecked.}

\section*{\centering Acknowledgements}
%
Thomas Valk and Jesper Meijerink helped design and perform the experiments.
Georgios Papaioannou and Arjo Loeve gave advice on the experimental design and
analyses.

\section{Introduction}
%
This paper reports on the vibration experienced by infants of different ages
when transported in cargo bicycles and strollers. Vibration can be related to
discomfort and might lead to negative health consequences. However, the topic is
poorly addressed in scientific literature, and only a few studies focus on the
effect of vibration on babies. To measure the actual vibration transmitted to
the babies, we equipped three strollers and two cargo bicycles with inertial
measurement units (IMU) and conducted several experiments across different road
surfaces and travelling speeds, using dummies representing the size of 0, 3, and
9 months old babies. We present analysis in the time and frequency domains,
allowing us to compare vertical accelerations at the baby-seat interface, as
recommended by ISO-2631-1. We investigate the influence of different variables
on vibration, such as type of vehicle, baby seat, travelling speed, dummy size
and mass, and road surfaces.

\section{Methods}
%
\subsection{Experimental Methodology}
%
In this section, we describe the measurement equipment used and the protocol
followed during the experimental campaign.

\subsubsection{Description of Test Equipment}
%
We conducted the experimental campaign using three different strollers, two
cargo bicycles, and two baby seats, chosen for their popularity and/or
distinctive features. The test involved three baby dummies representative of
various ages (different sizes and masses).

\paragraph{Strollers}
%
\begin{description}
  \item[Maxi-Cosi Street Plus] Among the most popular brands, this stroller comes
  with a cot configuration (0-3 months) and a baby seat option. It has large
  wheels, with only a marginal suspension system.
  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
  \item[Stokke BABYZEN YOYO 0+] It is the smallest foldable stroller on the
  market, it has only a marginal suspension system and smaller wheels compared
  to the other strollers on the market. It can be considered the ideal choice
  for holidays, being one of the few buggies that can be taken as hand
  luggage on the plane.
  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
  rented for the experiment})
  \item[Bugaboo Fox 5] It is featured by large wheels, and a suspension system
  which makes it an all-terrain stroller (according to the manufacturer). It has
  a large puncture-proof tyres and an air-permeable mattress.
  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
  website})
\end{description}

\paragraph{Cargo Bicycles}
%
\begin{description}
  \item[Urban Arrow Bicycle] This is a popular electric cargo bicycle in The
  Netherlands. This vehicle has two inline wheels which makes it roll into the
  curve like a regular bicycle. It is featured by a long frame that can carry
  loads usually placed in between the rider and the front wheel. It can fit
  various accessories, including baby seats, rain covers, etc.
  (\href{https://urbanarrow.com/}{Urban Arrow website})
  \item[Keiler Tricycle] This is a tadpole (two wheels in the front, one in the
  rear) cargo tricycle without electric assist. This vehicle will not roll in
  curves. However, differing road surface unevenness at the left and right front
  wheel will induce lateral roll and lateral acceleration in infants. We
  added masses in specific locations to simulate the presence of an electric
  motor and battery package.
 (\href{https://kashop.nl/product/keiler-bakfiets/}{Product Webpage}) 
\end{description}

\paragraph{Baby Seats}

These baby seats were mounted in the cargo bay of the two cargo bicycles.
%
\begin{description}
  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] This seat can be adapted to
    cargo bicycles with a proper fixing system (e.g. ``Urban Arrow Baby Car Seat
    Adapter''). It comes with an integrated suspension system which is part of
    the adapter.
    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi Webpage})
  \item[Melia Baby Shell]. The baby seat is meant for babies from 2 to 9 months,
    specifically designed for cargo bikes.
    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia Webpage})
\end{description}

We conducted tests using three different dummies, of various sizes and masses
according to the desired ages of 0, 3 and 9 months. We considered the use of
``crash test dummies'' which are designed and commonly used to test
child seats in cars in crash conditions. However, the nearest available body
sizes for crash test dummies were a 6-weeks Q-dummy, a 6-months Crabi dummy, and a
12-months Q-dummy. These 3 dummies are of a fundamentally different design,
hampering comparison, and do not match the desired body size. Moreover, these
child dummies have dynamic properties designed for crash conditions, and use
scaling of adult biomechanical data, rather than child data.
Testing with real children would be unethical for the most severe conditions
tested, and would create challenges in terms of reproducibility.
Hence we bought and adapted dummies available in a wide range of postures. We
bought ``reborn'' dummies from a webshop specialising in dolls and dummies
(\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). We filled the dummies
with cat litter sand to reproduce the exact weight needed for testing. Cat
litter sand indeed features smooth and round-shaped grains, which do not
damage the dummies' material (fabric and plastic). The weight and body height of
the dummies are average measures for children of exactly 0, 3 and 9 months old.
We wanted to use the measurements from Steenbekkers \cite{Steenbekkers1993}. But
the researchers provided the results only per three-month group, which did not fit our
age categories. Therefore, we decided to use the growth charts to determine the average weight
and body height at the right ages. Growth charts (`groeidiagrammen') are used by
doctors to assess the growth of babies. The average weight at 0 months and the
average body height at all three ages are derived from Dutch growth charts.
Measurements of Dutch children are used because the Dutchies are the target group of
VeiligheidNL. Dutch children are also the tallest in Europe. The average weight
of 3 and 9 months children is derived from French growth charts. French children
are the smallest in Europe. At 3 months, the weight difference is 4 ounces and
at 9 months, it is 3 ounces compared to Dutch children.  
%
\begin{description}
  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
  ``Andi Asleep'' (product code AW380008).
  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})
  \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
  ``Asia - Limited Edition'' (product code 300287).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=2556&group_id=10000176&lang=NL}{Webpage})
  \item[Dummy 9 months] weight 8.90~\si{\kg}. Size 70~\si{\cm}. Dollkit 28'',
  ``Hailey'' (product code 304137).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=1974&group_id=10000133&lang=NL}{Webpage})
\end{description}

To achieve a realistic mass distribution in the body of the dummies, it is
important to fill each limb with the proper amount of sand. To do this, we
simplified the geometry of each body segment according to defined basic
geometric shapes: we assumed a sphere for the head, and cylinders for the torso,
upper arms, upper legs and lower legs, according to what was stated in
\cite{Snyder1977}. We also assumed an equal density of each limb, and we
rescaled the measurements of the limb segments reported in \cite{Snyder1977} to
match the dimensions of our dummies. In doing so, we were able to calculate the
volume of each segment, thus the mass of each limb of the dummies (assuming a
density of 1000~\si{\kg\per\cubic\meter}).

\subsubsection{Description of Measurement Equipment}

>>>>

% Style Guide
% - use British English, exceptions: stroller vs buggy or pram, sidewalk vs pavement
% - active voice is preferred over passive voice, minimize passive
% - use past tense to describe what we did
% - try to avoid subsub sections (keep to two layers)
% - use siunitx for all units, surround with brackets [\si{\meter}], note the
%   common definitions, e.g. \si{\kph}
% - use tilde ~ to prevent line breaks in words that should stay together, e.g.
%   something~\cite{} or ISO~2631-1
% - only use "significant" when referring to statistical significance
% - use "infant", not "baby"
% - use "bicycle" instead of "bike"
% - use "amplitude spectrum/spectra" for what we plot
% - use "standard" not "norm"
% - use the oxford comma
% - TODO: acceleration vs accelerations ?
% - Data breakdown terms are "Session", "Trial" (of specific "Scenario"),
%   "Repetition"
% -  Referencing: Figure~\ref{fig:name}, Equation~\ref{eq:name},
%    Section~\ref{sec:name}, Appendix~\ref{app:name}, Table~\ref{tab:name}
% - inline urls \href{https://www.e.com}{my hyperlink}
% - do not use [h] for figures except in appendix, let latex place them where it
%   wants
% - figures should be 300 dpi and sized to the actual physical dimension in the
%   paper
% Other Notes
% - be careful about editing autogenerated tables, they will be overwritten

@@

% hyperref settings for better looking links
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue,
}

% NOTE : Use as \si{\kph} or \si{\mps}
\def\kph{\kilo\meter\per\hour}
\def\mps{\meter\per\second}

\title{
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
  \vspace{2mm}
  \large{Prepared for VeiligheidNL}
}
% Gabriele as first, Jason as last, alphabetical for intermediate (discuss in meeting if other method desired
\author{
Gabriele Dell'Orto \and
Brecht Daams \and
Riender Happee \and
Georgios Papaioannou \and
Arjo J. Loeve \and
Jesper Meijerink \and
Thomas Valk \and
Jason K. Moore
}

@@

\color{red}
\section*{\centering Notice}
%
This report or its findings may not be shared outside of VeiligheidNL and
TU~Delft without further review of the methods and findings.
We also need to carefully consider possible adverse effects of dissemination. In
particular we need to consider:
%
\begin{itemize}
  \item System manufacturers being negatively affected by publication.
    Organisations like Consumentenbond typically give manufacturers access to
    draft test results, and give an opportunity to react. We can do this as
    well. We may now remove Brand and type information from this report. In a
    later stage we may test multiple products and then publish a comparison.
  \item Stimulating car use to transport infants and children. We don't want
    newspaper/online headlines which are overly alarming, and later turn out to
    be debatable.
\end{itemize}
\color{black}

\begin{abstract}
  Infants are transported in strollers and in baby seats mounted in cargo
  bicycles. The infants experience whole-body vibration during the associated
  walking and cycling trips, but there is little existing knowledge about
  associated comfort and health effects. To improve this, we measure the seat
  pan acceleration of five strollers and two styles of cargo bicycles with dummy
  infants representing ages 0 to 9 months over six different road surfaces of
  varying road roughness at typical travel speeds. The five strollers included
  three modern systems and two vintage systems with some level of suspension.
  One cargo bicycle had electric support enabling speeds up to 25~\si{\kph}. We
  report average seat pan acceleration for 78 different scenarios and
  investigate the effects of road surface, vehicle, seat type, and travel speed.
  Using the whole-body vibration ISO standards, we show that rough road
  surfaces, amplified by travel speed, may have health risks for travel
  durations as low as \SIrange{10}{30}{\min}. Stroller designs from 50 years ago
  significantly reduce vibrations, relative to most modern strollers we tested,
  indicating the need for return of suspension elements. Cargo bicycles ridden
  at the maximum electric bicycle speed over paver bricks can cause
  accelerations that should likely be avoided except for only the shortest of
  durations until more direct evidence of risks to infants is studied. Standards
  are needed for infant transport testing and evaluation, designers need to
  incorporate better suspension for infants, and research is needed to develop
  clear and direct connections to health and comfort effects.
\end{abstract}

\newpage

\tableofcontents

\newpage

\section{Introduction}
%Paragraph to introduce baby transport
When a baby is born, it is not able to walk. To move around or travel, it must
be either carried by adults or transported in a suitable means of wheeled
transport. Until about a century ago,  babies mainly stayed at home. This still
is customary in some non-Western cultures. A century ago, perambulators were
used to transport infants outdoors. However, mothers were advised that a playpen
in the garden is healthier than the use of a perambulator, partly because the
vibrations generated by a perambulator were deemed not comfortable and even
harmful for the baby~\cite{behrend1931}, even though in those days perambulators
had ample suspension. Since about 1970, cars became ubiquitous and the heavy and
sizeable perambulators became strollers: lighter and smaller products to enable
easy transportation in a car. Over the years, new means of transportation came
into use for infants: cars with a child car seat, bicycles with a bicycle seat
and cargo bicycles with either a car seat or a baby shell.

%Paragraph to introduce baby vibration in transportation
All means of transport cause vibration, which is transferred to the infant
sitting or lying in it. Unlike the advice in the 1930s, vibration is seemingly
not a subject of attention in the present design of these products. On the
contrary, modern strollers do not have much suspension and cargo bicycles which
generate more vibration are increasingly used for infants. Interestingly, in the
literature we could find little about the maximal vibration load that babies and
older children can receive during transport without discomfort or harm, and
vibrations generated by infant transport are also only sparsely investigated.
Therefore the effect of transport on infant comfort and health can not easily be
assessed. To establish the amount of vibration that infants are subjected to in
transportation products, we investigated the vibration that infants receive
during transport in strollers and cargo bicycles.

% Paragraph about motivation
Cycling, one of the active transportation modes, is advantageous for
health~\cite{Oja1998} and greatly contributes to reducing CO\(_2\) emissions,
congestion, and air pollution~\cite{Neves2019}. As a result, bicycles are
increasingly used as a means to deliver goods to consumers, and also for daily
commuting to work and personal matters (shopping, commuting with
children/infants, and others). Among all journeys in the EU, 20-40\% are by
bicycle or on foot, with bicycle trips most frequent in the Netherlands,
Denmark, and Sweden and less frequent in Finland. Various countries and
employers provide incentives to increase the use of bicycles. However, some
challenges need to be overcome to secure the wide acceptance and use of active
transportation modes. One of these challenges is the comfort levels experienced
by riders and passengers (i.e., infants/children in cargo bicycles), which is a
multifaceted aspect~\cite{ayachi2015identifying} and critical for the wide
acceptance and use of bicycles as a daily means of transport. Meanwhile, this is
a topic that is of great interest and requires attention when it comes to
infants' transportation with strollers or bicycles.

% Paragraph about comfort in bicycles
The research on cyclist comfort is a natural starting point for investigations
of similar road-induced vibrations for infants.
Comfort on bicycles~\cite{too1990biomechanics} is mainly affected by physical
comfort and the impact of environmental factors (weather, geometry of the route,
and road roughness).  
Physical comfort is related to mechanical (bicycle and component design),
biomechanical (whole-body vibrations, human body dynamics, and kinematics) and
physiological factors (individual characteristics, e.g. sex, body size, weight
and others).
While there is extensive literature exploring the impact of environmental
factors (i.e., irregular road surface quality, weather conditions) on cyclists'
comfort~\cite{Stinson2003,Hagemeister2003,ayachi2015identifying,Verhoeven2017,Teixeira2020},
there is limited work on understanding the biomechanical and physiological
factors of comfort while being carried by bicycle (infants/children in bicycle
seats, on cargo bicycles, or in trailers). A particular concern is the transport
of infants under one year, who cannot well express any experience of discomfort
or pain.
Similar concerns are raised when it comes to strollers, where infants are also
exposed to vibrations induced by roads. 
In this paper, we will explore biomechanical comfort by assessing the whole-body
vibrations that could be experienced by transported infants both in cargo
bicycles and strollers, and evaluating potential health risks and discomfort
that might arise.

% Paragraph about transmission of vibrations
Biomechanical comfort is mostly related to the vibrations induced by road
irregularities and transmitted via the vehicle to the human body and head while
being driven~\cite{too1990biomechanics}. 
According to the literature, road irregularities are a critical factor for the
amplitude of the resulting vibrations experienced by the bicyclists and
passengers, as the vibrations induced on the body and head are not efficiently
isolated due to the lack of or inadequate suspension systems in most of the
bicycle models~\cite{vasudevan2017comparison} or strollers.
The bicycle or stroller design and its specific configuration can affect the
sitting posture, and eventually the transmissibility of the
vibrations~\cite{Brand2020,Verma2016}.
The sitting posture can also vary in case of children/infants who may be
transported sitting or lying down in a different posture and location than the
cyclist (e.g. above a wheel when in a bicycle seat) and in/on a different `seat'
(a car seat, bicycle seat, stroller seat, or cot). 
These all influence the level of whole-body vibrations and the transmission of
the vibrations from the seat to the body and head.
Furthermore, the amplitude of the vibrations experienced by
bicyclists/passengers/transported infants while biking or being transported in a
stroller may increase because of increased travelling speed either due to
running with a stroller or due to the increased power offered by electric
bicycles (with and without trailers).
For the latter, the average speed of electric bicycles and speed pedelecs is
19\% higher (21.0~\si{\kph} and up to 63\% higher (28.1~\si{\kph}),
respectively, than the average speed of conventional bicycling~\cite{SWOV2022}.
The intensity of these vibrations could become even more critical with the
change of load, which could be related with age and size of the infant/children
transported. However, there is limited literature exploring the whole-body
vibrations of infants and children being transported by bicycles with trailers,
cargo bicycles, stroller seats and others
~\cite{Ota2012,Ota2014,Kanya-Forstner2020, vanDriessche2018,
Schwanitz2020,MalteChildComfort2022}.
At the same time, the available literature is mostly focusing on comfort rather
than health risks.

% Paragraph about children in bicycles
One of the research fields closely related to vibrations acting on infants
during transportation is that of inflicted head injury by shaking trauma
(IHI-ST). However, there is a lack of reliable, applicable, validated injury
thresholds for assessing IHI-ST risks~\cite{hutchinson2024modeling}. Similarly,
even if there are significant indications that the vibration amplitude affects
comfort in bicycles or strollers, there are no standard assessment methods or
guidelines available with regards to their design. ISO~2631~\cite{ISO2631}, the
international standard for assessing whole-body vibrations, was derived using
datasets on motion platforms, adults as human participants and sitting postures
which are adopted in passenger vehicles rather than on bicycles.
This inconsistency was captured by Gao~et~al.~\cite{Gao2018}, who derived
different limits of comfort for adults riding on bicycles based on their
subjective feedback, compared to the vibration limits suggested by
ISO~2631-1.
In addition, the exposure time to the vibrations is not considered as a factor
of comfort by the ISO~2631-1, despite having a clear impact on health risks
according to the European Directive (2002/44/EC, 2002)
\cite{directive2002directive}.

% Paragraph Potential effects of vibrations on adults
Despite the lack of clarity with regards to comfort assessment or inflicted head
injury by shaking trauma for children/infants on bicycles, there are clear
indications in the literature that these should be explored and considered.
About 36\% of males and 42\% of females in a total sample of 900 people had
various complaints about comfort~\cite{groenendijk1992sitting}.
Discomfort for both men and women occurred even during short bicycle trips
(\SIrange{3}{10}{\kilo\meter}). However, results from research into comfort of
adult cyclists can not be applied directly to infants or children sitting or
lying in transportation systems.

Schwanitz~et~al.~\cite{Schwanitz2020} assessed accelerations in a child bicycle
trailer riding over smooth asphalt, gravel, and cobblestones using ISO~2631-1
weighted RMS vertical accelerations.
Anthropomorphic children shaped sandbag dummies (baby and toddler sizes) were
used as lumped masses. According to the results, tyre pressure and the number of
passengers had no significant effect on vibration magnitude, but road surface
and travel speed did. 
The baby sized dummy (5~\si{\kilo\gram}) experienced 20\% higher vibration than
the toddler sized dummy (10~\si{\kilo\gram}), while the measured values
generally exceeded the ISO~2631-1 vibrational comfort of adults.
Rothhämel~et~al.~\cite{MalteChildComfort2022} conducted measurements using a
trailer seat and a tadpole configuration three-wheel cargo bicycle on smooth
asphalt and cobblestones for speeds between \SIrange{10}{20}{\kph}. 
After weighting the accelerations using ISO~2631-1 methods, they found a large
increase of the vibration amplitude on cobblestones compared to asphalt on the
same speed range. The child trailer exhibited larger weighted RMS accelerations
than the cargo bicycle with the child seat between the front wheels. 
Both the trailer and cargo bicycle child seats had generally larger magnitude
vibrations than experienced in an automobile seat travelling at 30~\si{\kph} on
a rough road \cite{gromadowski2013analysis}. Rothhämel and
Liu~\cite{rothhamel2023comfort} conducted measurements with a
6.5~\si{\kilo\gram} mass representing an infant with various tyre pressures. All
their values fell into the ``extremely uncomfortable'' zone for the ISO~2631-1.

In addition to the studies with dummies or lumped masses representing
infants, Kanya-Forstner~\cite{Kanya-Forstner2020} measured acceleration in
bicycle child trailers with human subjects aged 12 months to 6 years over
asphalt and gravel terrain (averaged speed of 12~\si{\kph} over the
20~\si{\minute} ride). 
According to the health assessment using ISO~2631-1, the vibrations are similar
to the ones experienced in car seats in vehicles and illustrated moderate or low
health risk for a 2~\si{\hour} duration.
On the other hand, if not corrected for duration, the values point to moderate
and high risks. The terrain type had the greatest influence on vibration
exposure levels followed by trailer type, while gel cushions as support did not
significantly influence vibration measured at the seat/pan interface. Hence,
there is a need to re-focus on the impact of vibrations on infants and
children's health and comfort~\cite{rybarczyk2020physiological} to ensure the
safe, comfortable and wide use of bicycles.

% Don't edit, working to change the following paragraph
In the context of infants transportation with stroller seats, Kok
Siong~\cite{lim2018study} carried out an indoor and an outdoor experiment to
capture the vibrations transmitted onto the seat and backrest of a baby
stroller, using weights from \SIrange{4}{14.14}{\kilo\gram}, and  a child
subject of 10.30~\si{\kilo\gram} as well as a dummy weighing
10.30~\si{\kilo\gram}. 
The comfort levels for the indoor testing were labelled as `Fairly
uncomfortable' to `A little uncomfortable', but the outdoor testing resulted in
`Extremely uncomfortable' and `Fairly uncomfortable' values. They used both a
child and dummy for the experiments, identifying similar patterns. However, the
results still consider ISO~2631-1 standard, which is designed for adults and
specific postures. In a similar research, Sierzputowski~
et~al.~\cite{sierzputowski2021pilot} investigated vibrations induced in a modern
and
an older stroller, when moving on different surfaces: asphalt road, concrete
paving blocks, concrete plates, dirt road, lawn and damaged concrete. The
obtained weighted RMS acceleration values based on ISO~2631-1 were several times
in the range of the highest discomfort (>2~\si{\mps\squared}). 
Another research which included also children as test subjects was conducted by
Okajima~et~al.~\cite{okajima2020dynamic} measuring vibrations that seven
children received, sitting upright in a stroller, when riding over a protrusion
(13x60 mm) with either one wheel or two wheels. 
The children were 3 to 6 years old, boys and girls, weighing
\SIrange{15.94}{19.96}{\kilo\gram} and measuring
\SIrange{98.0}{112.4}{\centi\meter} in length. 
Based on the results, the infant’s head and chest exhibit strong vibrations at
1~\si{\hertz} along all three axes (x,y and z), vibrate easily along the
y-direction at 2~\si{\hertz}, and are less likely to vibrate at more than
8~\si{\hertz}. 
This result is critical as this range of frequencies is very common in bicycles
and strollers. However, they did not assess the comfort and the health risk when
the children were exposed to these vibrations. 
Despite significant research on the effect of whole-body vibrations on
children's comfort, there is limited research on infants.

This paper reports on the vibration induced on infants of different ages when
transported in strollers and cargo bicycles. 
Vibration can be related to discomfort and might lead to negative health
consequences. However, the topic is poorly addressed in scientific literature,
and only a few studies focus on the effect of vibration on babies as reviewed
above. 
To measure the actual vibration transmitted to infants, we equipped five
strollers and two cargo bicycles with inertial measurement units (IMU) and
conducted 78 experiments on different road surfaces and travel speeds, using
dummies representing the size and mass of 0, 3, and 9 months old infants.
We present results in the time and frequency domains, which allows comparing
vertical accelerations at the baby-seat interface, as recommended by ISO~2631-1
standards for vibration discomfort.
We investigated the influence of different variables on vibration, such as type
of vehicle, baby seat, travelling speed, dummy size and mass, and road surfaces
and provide recommendations to users, designers, and future researchers based on
the findings.

\section{Methods}
%
\subsection{Test Equipment}
%
Vibration measurements were conducted at approximate constant speed using five
different strollers, two cargo bicycles, and two baby
seats~\footnote{Appendix~\ref{app:equipment} provides figures and technical
descriptions of all the strollers and cargo bicycles.}, chosen for their
popularity and/or distinctive features:

\begin{description}
\item[Strollers] A selection of vintage and modern strollers for carrying
infants. The modern strollers are configurable as cots for newborns and as seats
for older infants.
%
\begin{description}
  \item[Maxi-Cosi Street Plus] This stroller comes
  with a cot configuration (0-3 months) and an infant seat option. It has large wheels, with only a marginal suspension system.
  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the
  market. It has only a marginal suspension system and smaller wheels compared to those of other strollers available on the market.
  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
  rented for the experiment})
  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system
  that makes it an all-terrain stroller according to the manufacturer. It has large puncture-proof tyres and an air-permeable mattress.
  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
  website})
  \item[Green Machine] An unknown brand vintage perambulator, dating
  approximately from the 1970's that includes a leather strap suspended cot in a
  metal frame. The wheels are relatively large in diameter compared to the
  modern strollers.
  \item[Old Rusty] An unknown brand vintage seat-style stroller from
  approximately the 1970's that includes a metal spring suspension system and
  wheels that are slightly larger than the modern strollers.
\end{description}
\item[Cargo Bicycles] Two modern Dutch ``bakfietsen'' in which different baby
seats can be mounted.
%
\begin{description}
  \item[Urban Arrow Bicycle] A popular electric cargo bicycle in The
  Netherlands. This vehicle has two inline wheels which makes it roll into
  curves like a regular bicycle. It is featured by a long frame that can carry
  loads (e.g. a child in a car seat or baby shell) placed in between the rider
  and the front wheel. 
  (\href{https://urbanarrow.com/}{Urban Arrow website})
  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the
  rear) cargo tricycle  without electric assist. This vehicle will not roll into
  curves. However, differing road surface unevenness at the left and right front
  wheel will induce lateral roll and lateral acceleration in infants. We added
  masses in specific locations to simulate the presence of an electric motor and
  battery package. (\href{https://kashop.nl/product/keiler-bakfiets/}{Product
  Webpage}) 
\end{description}
\item[Baby Seats] These two baby seats were mounted in the cargo bays of the two
cargo bicycles.
%
\begin{description}
  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to be
  mounted on cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow
  Baby Car Seat Adapter''). Comes with an integrated suspension system. The same
  adapter was used in both cargo bicycles.
    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi
    Webpage})
  \item[Melia Baby Shell] Baby seat specifically designed for cargo bicycles
  meant for babies from 2 to 9 months old. Mounted to the seat platform in both
  cargo bicycles.
    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia
    Webpage})
\end{description}
\end{description}

The tests involved three baby dummies with sizes and weights representative of
newborns and 3 and 9 month old infants. Newborns (`0 months') are the youngest
(smallest, lightest) children that are transported in strollers with a cot.
Three month old infants are the youngest (smallest, lightest) children that are
transported in cargo bicycles, fixated in a baby car seat or baby shell. Nine
month old infants are the youngest (smallest, lightest) that can sit up straight
by themselves and thus can be transported sitting up straight, in a stroller
with a seat or on the bench of a cargo bicycle.

We considered the use of ``crash test dummies'' (also known as anthropomorphic
test devices or ATD's) which are designed and commonly used to test child seats
in car crash tests. However, the nearest available body sizes for crash test
dummies were a 6-weeks Q0-dummy, a 6-months Crabi dummy, and a 12-months Q-dummy
(Humanetics, Farmington Hills, USA). These 3 dummies are of a fundamentally
different design, hampering comparison, and did not match the desired body
sizes. Moreover, these child dummies have dynamic properties designed for crash
conditions, and they were designed based on scaling of adult biomechanical data
rather than child data, so in that respect there is no benefit over other
dummies.

Testing with real infants would be unethical, and would create challenges in
terms of reproducibility. Hence we bought and adapted ``reborn'' dummies
available in a wide range of postures from a webshop specialising in dolls and
dummies (\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). The dummies were
filled with a mixture of cat litter sand and water to reproduce the exact
weights needed for testing. Cat litter sand features smooth and round-shaped
grains, which do not damage the dummies' materials (fabric and plastic). The
weight and body height of the dummies were made to match the average measures
for children of 0, 3 and 9 months old.

We wanted to use the measurements from Steenbekkers~\cite{Steenbekkers1993}.
However, this research provided the results only per three-month group, which
did not fit our age categories. We decided to use the growth charts used by
clinicians to assess infant growth to determine the average weight and body
height at the right ages. The average weight at 0 months and the average body
height at all three ages are derived from Dutch growth charts. We used
measurements of Dutch children because they are the target group of the project
funder, VeiligheidNL. Dutch children are also the tallest in Europe. We derived
the average weight of 3 and 9 months old children from French growth charts.
French children are the smallest in Europe. At 3 months, average Dutch children
weigh 113 gram more than average French children and at 9 months, the difference
is 85 gram. The following lists the dummies used:
%
\begin{description}
  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
  ``Andi Asleep'' (product code AW380008).
  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})

  \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
  ``Asia - Limited Edition'' (product code 300287).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=2556&group_id=10000176&lang=NL}{Webpage})
  \item[Dummy 9 months] weight 8.90~\si{\kg}. Size 70~\si{\cm}. Dollkit 28'',
  ``Hailey'' (product code 304137).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=1974&group_id=10000133&lang=NL}{Webpage})
\end{description}

To achieve a realistic mass distribution in the body of the dummies, each limb
was filled with a proper amount of wet sand (for the 0-month dummy, water was
added to achieve the correct weight). To do this, we simplified the geometry of
each body segment according to the defined basic geometric shapes: a sphere for
the head, and cylinders for the torso, upper arms, upper legs and lower legs,
according to what was stated in~\cite{Snyder1977}. We also assumed an equal
density for each limb, and we rescaled the measurements of the limb segments
reported in \cite{Snyder1977} to match the dimensions of our dummies. In doing
so, we were able to calculate the volume of each segment, thus the mass of each
limb of the dummies (assuming a density of 1000~\si{\kg\per\cubic\meter}).

\subsection{Measurement Equipment}
%
Linear accelerations and angular velocities were measured tri-axially using
Consensys Shimmer3 IMUs with a Consensys Base 6U.01 dock (Shimmen Sensing,
Dublin, Ireland). The IMUs were updated to firmware version LogAndStream v0.11.0
and managed via the software ConsensysBASIC v1.6.0-64bit on a Dell 7310 laptop
with Microsoft Windows 10. We 3D printed supports (material: PLA) for the
sensors to ensure a firm clamp between the sensor and the bicycle/stroller
tested (Small white and orange boxes visible in Figure~\ref{fig:sensors_UA}).
Each vehicle was equipped with five IMUs, as listed below. All the drawings
showing the vehicles and the sensors' location are reported in
Appendix~\ref{app:equipment}.
%
\begin{enumerate}
  \item \textbf{Rear Wheel} This IMU was placed on the wheel hub (cargo
  bicycles) or clamped to the wheel (strollers) for measuring the travel speed.
  The travelling (longitudinal) speed was derived according to:
  %
  \begin{align}
    v = \omega \cdot r
    \label{eq:long-speed}
  \end{align}
  %
  where \(\omega\) is the angular speed of the wheel (obtained from the IMU's
  gyroscope aligned with the wheel's axis) and \(r\) is the radius of the wheel.
  \item \textbf{Front Wheel} This IMU was mounted on the front wheel fork (the
  caster wheel for the stroller). This was the non-rotating measurement point
  closest to the ground. The purpose of this sensor was to measure the road
  roughness filtered out only by the tyres.  
  \item \textbf{Frame} On the cargo bicycle, an IMU was placed below the frontal
  cargo bay and clamped to the frame. This was to provide an understanding of
  the damping characteristics of the bicycle frame, together with an estimation
  of the effect of the suspension system. On the stroller, the IMU was taped
  under the baby seat.
  \item \textbf{Seat Head} IMU taped into the baby seat (on the soft mattress),
  directly in contact with the dummy's head. This IMU measured the vibration
  transmitted to the head contact point.
  \item \textbf{Seat Pan} This IMU was taped into the baby seat, at the
  interface between the dummy's buttock and the baby seat. It measured the
  vibration transmitted to the dummy's buttock.
\end{enumerate}
